The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-20 analysis/paper/paper.qmd
Generalize geocode function with location

# Add latitude and longitude information to theses data frame
emu_theses <- geocode_thesis_locations(emu_theses, "location")

>>>>

# Add latitude and longitude information to theses data frame
emu_theses <- geocode_thesis_locations(emu_theses, location = NULL)

 geocoded_data <- tidygeocoder::geocode(emu_theses,
      address = location,
      method = 'osm',
      lat = latitude ,
      long = longitude
 )
